The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2022-01-04 paper.tex
update

  The initial density profile of \Cref{disk-atm-sys} is shown in \Cref{density-profile}\
  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\

@@

  \begin{figure*}[h]
    \subfigure[The initial gaseous density profile along z-axis] % caption
    {
      \includegraphics[width=0.4\linewidth]{figures/fig__density-profile.png}
      \label{density-profile}
    }
  \caption{Captions}
  \end{figure*}

>>>>

  The density profile of \Cref{disk-atm-sys} is shown in \Cref{fig__initial-density-profile}\
  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\

@@

  \begin{figure}
    \includegraphics[width=1.0\linewidth]{figures/fig__initial-density-profile.png}
    \caption{The profile of $\rho_{\text{isoDisk}}(z)$ along z-axis.}
    \label{fig__initial-density-profile}
  \end{figure}

  \begin{figure}
      \includegraphics[width=1.0\linewidth]{figures/fig__numberDensityHistogram.png}
      \caption{The initial density distribution of the number density\
               for a settling ISM without jet source.} % caption
      \label{fig__numberDensityHistogram}
  \end{figure}
